Fig2: Candidate genes

### 2020-05-20 analysis/figure-2.Rmd
missing candidate gene list

```{r DEGs}
# summary DEG results from DESeq2
candidateDEGS <- read_csv("../results/suppletable1.csv") %>%
  filter(gene %in% candidategenes) %>%
  mutate(posneg = ifelse(lfc >= 0, "+", "-"),
         sex = recode(sex, "female" = "F", "male" = "M" ),
         tissue = recode(tissue, 
                         "hypothalamus" = "H",
                         "pituitary" = "P", "gonad" = "G")) %>%
  mutate(res = paste(sex, tissue, posneg, sep = "")) %>%
  select(gene, res, comparison)  %>%
  group_by(gene,  comparison) %>%
  summarize(res = str_c(res, collapse = " ")) %>%
  pivot_wider(names_from = comparison, values_from = res) %>%
  select(gene, control_bldg, bldg_lay, lay_inc.d3, inc.d3_inc.d9, inc.d9_inc.d17, hatch_n5, n5_n9)
candidateDEGS

@@

bcd <- plot_grid(b,c,d, ncol = 3, rel_widths = c(1,1,1), labels = c("B", "C", "D"), label_size = 8)

fig2 <- plot_grid(a,bcd, ncol = 1, labels = c("A"), label_size = 8, rel_heights = c(0.1,1))
fig2

>>>>

```{r DEGs}

# summary DEG results from DESeq2
candidateDEGS <- read_csv("../results/suppltable1.csv") %>%
  filter(gene %in% candidategenes) %>%
  mutate(posneg = ifelse(lfc >= 0, "+", "-"),
         sex = recode(sex, "female" = "F", "male" = "M" ),
         tissue = recode(tissue, 
                         "hypothalamus" = "H",
                         "pituitary" = "P", "gonad" = "G")) %>%
  mutate(res = paste(sex, tissue, posneg, sep = "")) %>%
  select(gene, res, comparison)  %>%
  group_by(gene,  comparison) %>%
  summarize(res = str_c(res, collapse = " ")) %>%
  pivot_wider(names_from = comparison, values_from = res) %>%
  select(gene, control_bldg, bldg_lay, lay_inc.d3, inc.d3_inc.d9, inc.d9_inc.d17, hatch_n5, n5_n9)
candidateDEGS

@@

bcd <- plot_grid(b,c,d, ncol = 3, rel_widths = c(1,1,1), labels = c("A", "B", "C"), label_size = 8)

fig2 <- plot_grid(bcd, a, ncol = 1, rel_heights = c(1,0.1))
fig2
